Robust Energy-Aware Routing with Uncertain Traffic Demands

### 2014-11-21 paper.tex
Add phase two description

\subsection{First Phase Description}
REAR sleep as many links as possible without losing much connectivity of graph. Originly,  we should
calculate impact of all the links and sleep the lowest one from the graph, then repeat calculate and remove
process until arrive some specific threhold. Obviously, it is NP-Hard, following is a heuristic algorithm.

@@

\subsection{Second Phase}
When we get the output graph from the first phase based on extend algebraic connectivity, it is time to compute
the robust routing.

@@

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

\end{thebibliography}

>>>>

\subsection{Algorithm Phase One}
REAR sleep as many links as possible without losing much connectivity of graph. Originly,  we should
calculate impact of all the links and sleep the lowest one from the graph, then repeat calculate and remove
process until arrive some specific threhold. Obviously, it is NP-Hard, following is a heuristic algorithm.

@@

\subsection{Algorihtm Phase Two}
Once we get the output network topology from the first phase based on extend algebraic connectivity, it is time to compute
the robust routing. We first calculate the demand-oblivious rouintg from the origin topology based on algorithm proposed 
by David pplegate[1]; and adjust routing in details according to the links we switched off in the final topology.

The demand-oblivious routing can be computed by a single LP with $O(mn^2)$ variables and $O(nm^2)$ constraints :
\begin{table}[!th]
	\begin{tabular}{ll}
		$\:\:$\quad\quad\ min $r$ \\
		$\:\:$\quad\quad\ $f_{ij}(e)$ is a routing \\
		$\:\:$\quad\quad\ $\forall$ links $l$: $\sum_m cap(m)t(l,m) \le r$ \\
		$\:\:$\quad\quad\ $\forall$ links $l$, $\forall$ pairs $i \rightarrow j$: \\
		$\:\:$\quad\quad\quad\quad\ $f_{ij}(l)/cap(l) \le p_l(i,j)$ \\ 
		$\:\:$\quad\quad\ $\forall$ links $l$, $\forall$ nodes $i$, $\forall$ edges $e = j \rightarrow k$: \\
		$\:\:$\quad\quad\quad\quad\ $\pi(l, link-of(e)) + p_l(i,j) - p_l(i,k) \ge 0$ \\
		$\:\:$\quad\quad\ $\forall$ links $l$, $m$: $\pi(l, m) \ge 0$ \\
		$\:\:$\quad\quad\ $\forall$ links $l$, $\forall$ nodes $i$: $p_l(i,i) = 0$ \\
		$\:\:$\quad\quad\ $\forall$ links $l$, $\forall$ nodes $i$, $j$: $p_l(i,j) \ge 0$ \\
	\end{tabular}
\end{table}
where the $cap(l)$ isthe capacity of link $l$; 
and $\pi(l,m)$ is the weights for every pair of links $l$, $m$; and the variables $p_l(i,j)$ for each link $l$ 
and OD pair $i$, $j$ is the length of the shortest path from $i$ to $j$ according to the link weights $\pi(l, m)$.

The routing we get indicate how to arrive destination node from source node for every OD pair in the origin topology.
What is different is that, the flow can be splited in the routing, i.e. there may be two paths ($path_1$, $path_2$)
both from source node $s$ to destination node $d$, and the optimal obilious routing trace 70\% traffic on 
$path_1$ and left on $path_2$. However splitting flow is hard handled, we take a transformation for this case like this:
when an flow is coming, there is 70\% probability we trace it on $path_1$, otherwise $path_2$.

Because all the routing is based on the origin topology, when switch-off links is done, we must adjust the routing 
as well. Take pair $(s, d)$ for example, the path in routing maybe like $s \rightarrow i \rightarrow j \rightarrow d$,
unfortunately link $i \rightarrow j$ is switched off in Phase One of Algorithm. For the final topology is still 
connected, we must can find another path from $i$ to $j$, such as $i \rightarrow k \rightarrow j$,
instead of the direct link $i->j$, then we just replace the routhing $s \rightarrow i \rightarrow j \rightarrow d$ with
$s \rightarrow i \rightarrow \rightarrow k \rightarrow j \rightarrow d$.
Find the path between two nodes of switch-off link is easy by Dijkstra Algorithm on the final topology.

And this is our implementation:
\begin{table}[!th]
\begin{tabular}{ll}
\hline
\textbf{Algorithm REAR : Phase Two}\\
\hline
$\:\:$\textbf{Input:} $G(V,E)$ which is the origin topology;\\
$\quad\qquad\quad$ $S$ which is the switch-off links set generated by Phase One;\\
$\:\:$\textbf{Output:} $Rouing$ Robust Energy-Aware Routing on new topology\\
$\:\:$1:\ $G^* \leftarrow G(V, E-S)$;\\
$\:\:$2:\ $Replace \leftarrow \emptyset$;\\
$\:\:$3:\ \textbf{for} {each link $l$ in $S$}\\
$\:\:$4:\quad\ $ls \leftarrow node of l$, $ld \leftarrow the other node of l$;\\
$\:\:$5:\quad\ $Replace[ls, ld] \leftarrow find path form ls to ld on G^*$;\\
$\:\:$6:\ $Routing \leftarrow run LP in CPLEX, fetch routing by parsing result$;\\
$\:\:$7:\ \textbf{for} {each r in Routing}\\
$\:\:$8:\quad\ \textbf{if} $l \in S in r $\\
$\:\:$9:\quad\ \quad\ $s \leftarrow source of r$, $d \leftarrow destination of r$;\\
$\:\:$10:\quad\ \quad\ $r \leftarrow r[s, ls] + Replace[ls,ld] + r[ld,d]$;\\
$\:\:$11:\ \textbf{return} Routing;\\
\hline
\end{tabular}
\end{table}

@@

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
\end{thebibliography}
